---
title: "HW9_answer"
author: "Guojing Wu"
date: "4/29/2019"
output:
    pdf_document:
    highlight: default
    number_sections: true
    citation_package:
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
fontsize: 10pt
geometry: margin=1in
bibliography:
biblio-style:
header-includes:
- \usepackage{indentfirst}
- \usepackage{graphicx}
- \usepackage{geometry}
- \usepackage{subfigure}
- \usepackage{amsmath}
- \usepackage{listings}
- \usepackage{tikz}
- \usetikzlibrary{matrix}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      message = F, 
                      warning = F, 
                      comment = "")
library(tidyverse)
theme_set(theme_bw())
```

## Problem 1. Determine the survival and density function

Notate survival function as $S(x)$, cumulative hazard function as $H(x)$, cumulative density function as $F(x)$ and probability density function as $f(x)$:

$$
\begin{split}
h(x) &= \frac{2x}{1+x^2} \\
H(x) &= \int_{0}^{x}h(t)dt = ln(1+x^2) \\
S(x) &= exp(-H(x)) = \frac{1}{1+x^2} \\
F(x) &= 1 - S(x) = 1- \frac{1}{1+x^2} \\
f(x) &= \frac{d}{dx}F(x) = \frac{2x}{(1+x^2)^2}
\end{split}
$$

## Problem 2. Write out table and calculate estimation of survival function

|$t_i$|$n_i$|$d_i$|$c_i$|$\hat{\lambda_i}$|                                $\hat{S}(t)$|                           $\tilde{H}(t)$| $exp(-\tilde{H}(t))$|
|----:|----:|----:|----:|----------------:|-------------------------------------------:|----------------------------------------:|--------------------:|
|    1|   10|    1|    0|   $\frac{1}{10}$|           $1*(1-\frac{1}{10})=\frac{9}{10}$|                           $\frac{1}{10}$|0.905|
|    2|    9|    2|    0|    $\frac{2}{9}$| $\frac{9}{10}*(1-\frac{2}{9})=\frac{7}{10}$| $\frac{1}{10}+\frac{2}{9}=\frac{29}{90}$|0.725|
|    4|    7|    0|    1|                0|                              $\frac{7}{10}$|                          $\frac{29}{90}$|0.725|
|    5|    6|    0|    1|                0|                              $\frac{7}{10}$|                          $\frac{29}{90}$|0.725|
|    6|    5|    1|    0|    $\frac{1}{5}$|$\frac{7}{10}*(1-\frac{1}{5})=\frac{14}{25}$|$\frac{29}{90}+\frac{1}{5}=\frac{47}{90}$|0.593|
|    7|    4|    0|    1|                0|                             $\frac{14}{25}$|                          $\frac{47}{90}$|0.593|
|    8|    3|    0|    1|                0|                             $\frac{14}{25}$|                          $\frac{47}{90}$|0.593|
|    9|    2|    0|    1|                0|                             $\frac{14}{25}$|                          $\frac{47}{90}$|0.593|
|   10|    1|    0|    1|                0|                             $\frac{14}{25}$|                          $\frac{47}{90}$|0.593|

Problem 3. Tongue data

```{r}

```


## Code
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```